\bf\mftitle

### 2011-02-28 doc/jInfer/autoeditor/autoeditor.tex
Documentation: AutoEditor.

\begin{figure}
\centering\includegraphics[scale=0.65]{uml_derived_classes}
\caption{Class diagram for the derived classes, not showing members of classes from figure \ref{uml_base_classes} to keep this diagram simple.} \label{uml_derived_classes}
\end{figure}

@@

\code{StatePickingVisualizer} is trivial extension of \code{PluggableVisualizer}. It has no additional methods. Its constructor has additional two arguments, superinitial and superfinal states as we want to distinguish these states in displayed automaton.\
And upon construction, it just adds \code{VertexPickingGraphMousePlugin} to the plugins of \linebreak \code{PluggableVisualizer}. Purpose of this plugin is to allow user to pick some state of automaton and then call \code{guiDone()} method on instance of \code{AbstractComponent}. For description of \code{guiDone()} method, see \ref{subsubsection:AbstractComponent}.\\

@@

>>>>

\begin{figure}
\centering\includegraphics[scale=\myscale]{uml_derived_classes}
\caption{Class diagram for the derived classes, not showing members of classes from figure \ref{uml_base_classes} to keep this diagram simple. Also not showing signatures of constructors of StatePickingVisualizer and StatePickingVisualizer for their length.} \label{uml_derived_classes}
\end{figure}

@@

\code{StatePickingVisualizer} is trivial extension of \code{PluggableVisualizer}. It has no additional methods. Its constructor has several additional arguments. Their description follows.
\begin{verbatim}
public StatePickingVisualizer(
    Layout<State<T>, Step<T>> layout,
    Transformer<Step<T>, String> edgeLabelTransformer,
    AbstractComponent<T> component,
    State<T> superinitialState,
    State<T> superfinalState)
\end{verbatim}
\begin{itemize}
	\item \code{layout} - Instance of \code{Layout} which will be provided to the constructor of parent \code{Visualizer} class.
	\item \code{edgeLabelTransformer} - Transformer to convert automaton edges to their string representations.
	\item \code{component} - Instance of \code{AbstractComponent} to call \code{guiDone()} method on, when a state is picked.
	\item \code{superinitialState} and \code{superfinalState} - Superinitial and superfinal states as we want to distinguish these states in displayed automaton.
\end{itemize}

Upon construction, it just adds \code{VertexPickingGraphMousePlugin} to the plugins of \linebreak \code{PluggableVisualizer}. Purpose of this plugin is to allow user to pick some state of automaton and then call \code{guiDone()} method on instance of \code{AbstractComponent}. For description of \code{guiDone()} method, see \ref{subsubsection:AbstractComponent}.\\

@@

Signature of constructor and description of arguments follow.
\begin{verbatim}
public StatesPickingVisualizer(Layout<State<T>, Step<T>> layout, Transformer<Step<T>, String> edgeLabelTransformer)
\end{verbatim}
\begin{itemize}
	\item \code{layout} - Instance of \code{Layout} which will be provided to the constructor of parent \code{Visualizer} class.
	\item \code{edgeLabelTransformer} - Transformer to convert automaton edges to their string representations.
\end{itemize}
